\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-05 paper/mswp2012-proposal.tex
Trying to add some more justifications for used methods

\subsection{User Centered Design}
\label{subsect:ucd}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

\subsection{Experimental Horizontal Prototyping}
We decided for a combination of experimental and horizontal prototyping as software development method.

@@

Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Jakob Nielsen \citep[Page 195ff]{nielsen1994}. It involves participants thinking aloud as they perform certain tasks. The participants are asked to say whatever they are thinking about, looking at, doing or feeling while performing the tasks. Observers take notes of everything the participant says during the scenario without attempting to interpret their claims. The sessions are usually recorded to enable you to go back later and connect the claims with the tasks the participant was currently performing. The purpose of this method is to make assumptions explicit. By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions. It helps reveiling \emph{why} users do something. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems.

@@

Empirical study of the needs of the main stakeholders in the project is essential. By means of surveys and interviews we try to identify requirements and hope to get answers to the following (and more) questions:

\begin{itemize}
\item What do end users need/want? What is negligible and can therefore be omitted?
\item What do they miss in actual systems?
\item How do they wish to interact with the system?
\item What are the needs of the different business partners?
\item Which systems are currently in use at the partners processes?
\item How would they improve their current systems?
\end{itemize}

@@

Certainly we do not have to reinvent the wheel. Therefore a detailed literature research has to be carried out to find possible approaches that can be reused. By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others projects. The literature research part aims at answering the following questions

\begin{itemize}
\item Which techniques are already in use or have been introduced in the field of
\begin{itemize}
\item healthcare applications?
\item ubiquitous systems?
\item user centered design?
\item usability engineering?
\end{itemize}
\item Which of the found techniques can be reused?
\item What can be improved?
\end{itemize}

>>>>

\subsection{User Centered Design}
\label{subsect:ucd}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System because it is a structured method that involves the end users throughout all stages of the design and development of our system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

\subsection{Experimental Horizontal Prototyping}
We decided for a combination of experimental and horizontal prototyping as software development method because it perfectly fits into the overall procedure model. By creating an horizontal prototype in an early state and iterating it with the information gathered from our users we aim at creating a highly usable product with reasonable costs.

@@

Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Jakob Nielsen \citep[Page 195ff]{nielsen1994}. It involves participants thinking aloud as they perform certain tasks. The participants are asked to say whatever they are thinking about, looking at, doing or feeling while performing the tasks. Observers take notes of everything the participant says during the scenario without attempting to interpret their claims. The sessions are usually recorded to enable you to go back later and connect the claims with the tasks the participant was currently performing. The purpose of this method is to make assumptions explicit. By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions. \\

We choose to use Thinking Aloud during the conception of the Modern Health Care System because it helps reveiling \emph{why} users do something. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems and this ultimately leads to a better system and reduced costs.

@@

Empirical study of the needs of the main stakeholders in the project is essential. Creating a product that does either not suit the workflow of the desired users or doesn't gain any traction for viable business partners would be a failure of the project. By means of surveys and interviews we try to identify requirements at the beginning and aim at getting answers to at least the following questions:

\begin{itemize}
\item What do end users need/want? What is negligible and can therefore be omitted?
\item What do they miss in current systems?
\item How do they wish to interact with the system?
\item What are the needs of the different business partners?
\item Which systems are currently in use at the partners processes?
\item How would they improve their current systems?
\end{itemize}

@@

Certainly we do not have to and do not intent to reinvent the wheel with the Modern Health Care System, therefore a detailed literature research has to be carried out to find possible approaches that are already tested and can be reused. By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others and concentrate on the questions that haven't been answered yet. \\

The literature research part aims at answering the following questions:

\begin{itemize}
\item Which techniques are already in use or have been introduced in the field of
\begin{itemize}
\item healthcare applications?
\item ubiquitous systems?
\item user centered design?
\item usability engineering?
\end{itemize} 
\item Which of the found techniques can be reused?
\item What can be improved?
\item Which research questions are still open to answer?
\end{itemize}
